Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-15 programlogic.tex
reg ptsto fix

\paragraph{Register points-to} 
The assertion $\pfpointsto\rg\rv\rpts\qfrac$ ensures the ownership of the register $\rg$ naming the register value $\rv$. 
The fraction $\qfrac$ with value 1 asserts the unique ownership of the register mapping, and grants update permission on it, 
otherwise, any value $0 < \qfrac <1$ represents partial ownership granting readonly permission on the mapping.

>>>>

\paragraph{Register points-to} 
The assertion $\textsf{r}\;\mapsto_{\textsf{r}}\{q\}\;\textsf{rv}$ ensures the ownership of the register $\rg$ naming the register value $\rv$. 
The fraction $\qfrac$ with value 1 asserts the unique ownership of the register mapping, and grants update permission on it, 
otherwise, any value $0 < \qfrac <1$ represents partial ownership granting readonly permission on the mapping.
